R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
formalize the resources section

The story of R Markdown begins with Markdown, a markup language and formatting
syntax designed to be:

@@

### Resources

- http://ropensci.github.io/reproducibility-guide/sections/tools/
- http://shop.oreilly.com/product/0636920051435.do
- https://rviews.rstudio.com/2018/11/01/r-markdown-a-better-approach/
- https://rviews.rstudio.com/2017/01/25/r-markdown-for-the-enterprise/
- https://en.wikipedia.org/wiki/Markdown
- https://www.oreilly.com/library/view/the-art-of/9781593273842/ch15.html

>>>>

The story of R Markdown begins with
[Markdown](https://en.wikipedia.org/wiki/Markdown), a markup language and
formatting
syntax designed to be:

@@

# RESOURCES

The source and examples from this paper are available on GitHub:

https://github.com/colearendt/rmarkdown-for-reproducible-research

There are also many other interesting resources on this topic
which we did not have the opportunity to include:

- http://ropensci.github.io/reproducibility-guide/sections/tools/
- http://shop.oreilly.com/product/0636920051435.do
- https://rviews.rstudio.com/2018/11/01/r-markdown-a-better-approach/
- https://rviews.rstudio.com/2017/01/25/r-markdown-for-the-enterprise/
